Documentation FFI Sonar Simulator

### 2013-05-22 FFI-Simulator/ffi-simulator.tex
la2pdf commit - 2013:05:23	01:21:41	(Thu23.May)

@@

\subsection{Using only OpenGL for the simulator?}

\begin{figure}[b]
\begin{narrow}{-2.3cm}{-2.3cm}
\graphicsAI[drawing,width=\linewidth]{gfx/simulation_setup.png}
\end{narrow}
\caption{Two possible implementation strategies.}\label{implementation}
\end{figure}

>>>>

\subsection{Simulating a sonar scenario using optics}

\begin{figure}[b]
\begin{narrow}{-2.3cm}{-2.3cm}
\graphicsAI[drawing,width=\linewidth]{gfx/simulation_setup.png}
\end{narrow}
\caption{Two possible implementation strategies.}\label{simulation_setup}
\end{figure}

As a preliminary study we created a 3D model of a manta mine and a cylinder located on a flat ground surface (fig. \ref{simulation_setup}). Here we placed the camera 6 meters above the surface looking down on it. The light source was put at a 50\;m distance and set up without falloff, and the light hits the centre of the scene at an angle of 10$^\circ$. The manta mine was made according to specifications with 48\;cm height and 98\;cm ground diameter, the same applies to the cylinder. The distance between the two objects is 1\;m.

\begin{figure}[H]
\begin{minipage}[c]{0.49\linewidth}
\graphicsAI[drawing,width=\linewidth]{gfx/simulation_mask.png}
\end{minipage}\mbox{}\hfill
\begin{minipage}[c]{0.49\linewidth}
\graphicsAI[drawing,width=\linewidth]{gfx/simulation_object.png}
\end{minipage}
\graphicsAI[drawing,width=\linewidth]{gfx/simulation_optical.png}
\caption{Optical rendering.}\label{s}
\end{figure}

@@
